\begin{thebibliography}{1}

\bibitem{DHMM}
A. Seibel, S. Neumann, and H. Giese. Dynamic hierarchical mega models: com- prehensive traceability and its efficient maintenance. Software \& Systems Mod- eling, 9(4):493–528, 2010.

\bibitem{IEEEGlossary}
IEEE: IEEE Standard Glossary of Software Engineering Terminology, IEEE Std 610.12-1990

\bibitem{MEGAL1}
Jean-Marie Favre, Ralf Lämmel, and Andrei Varanovich. Modeling the Linguistic Architecture of Software Products.

\bibitem{MEGAF}
R. Hilliard, I. Malavolta, H. Muccini, and P. Pelliccione. Realizing Architecture Frameworks Through Megamodelling Techniques. In Proc. of ASE’10, pages 305–308. ACM, 2010.

\bibitem{MEGAL2}
Ralf Lämmel and Andrei Varanovich. Interpretation of Linguistic Architectur. Unpublished, 2014

\bibitem{TraceabilitySurvey}
S. Winkler and J. von Pilgrim. A survey of traceability in requirements engineer- ing and model-driven development. Software and System Modeling, 9(4):529– 565, 2010. 

\bibitem{MegaRuntime}
Thomas Vogel, Andreas Seibel, and Holger Giese. The Role of Models and Megamodels at Runtime.

\bibitem{ScopedTraceability}
Lago, P., Muccini, H., van Vilet, H.: A scoped approacht to traceability management. J. Syst. Stoftw. 82(1), 168-182 (2009)

\bibitem{TowardsAMegamodel}
J.-M. Favre and T. NGuyen. Towards a Megamodel to Model Software Evolution through Transformations. ENTCS, 127(3), 2004. Proc. of the SETra Workshop.

\bibitem{Pinheiro}
Pinheiro, F.A.C.: Requirements traceability. In: Sampaio do Prado
Leite, J.C., Doorn, J.H. (eds.) Perspectives on Software Require-
ments, pp. 93–113. Springer, Berlin (2003)

\bibitem{GotelFinkelstein}
Gotel, O.C.Z., Finkelstein, A.C.W.: An analysis of the require-
ments traceability problem. In: 1st IEEE International Require-
ments Engineering Conference (RE’94) Proceedings, pp. 94–101.
IEEE Computer Society, New York (1994)

\bibitem{RameshEdwards}
Ramesh, B., Edwards, M.: Issues in the development of a require-
ments traceability model. In: Proceedings of the IEEE Interna-
tional Symposium on Requirements Engineering, pp. 256–259.
IEEE Computer Society, New York (1993)

\bibitem{OED}
Simpson, J., Weiner, E. (eds.): Oxford English Dictionary, vol. 18,
2nd edn. Clarendon Press, Oxford (1989). ISBN 978-0-198-
61186-8

\bibitem{ModelTraceability}
Aizenbud-Reshef, N., Nolan, B.T., Rubin, J., Shaham-Gafni, Y.:
Model traceability. IBM Syst. J. 45(3), 515–526 (2006)

\bibitem{ISO/IEC42010}
ISO. ISO/IEC CD1 42010, Systems and software engineering
— Architecture description (draft), January 2010.

\end{thebibliography}